Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-31 TACAS2018/paper.tex
formatting

We use a CounterExample-Guided Inductive Synthesis (CEGIS)~\cite{jha-icse10,
DBLP:conf/pldi/Solar-LezamaRBE05} approach, which we enhance with
abstraction refinement and optimization resulting in the novel CEGIS-OR
(CEGIS with Optimization and Refinement).  This design uses an iterative
process where each iteration performs inductive generalization based on
counterexamples provided by a verification oracle.  Essentially, the
inductive generalization uses information about a limited number of inputs
to make claims in the form of candidate solutions about all the possible
inputs.  By using abstraction refinement, CEGIS-OR allows us to handle
complex systems, which are initially represented by coarse abstractions that
only get refined on demand.  Consequently, solutions that do not require a
high level of precision are obtained fast.  Since the use of coarse
abstractions may result in low-quality candidate solutions (i.e., candidates
that fail the specification on a very large number of inputs), we use
optimization techniques after each inductive generalization phase to improve
the produced candidates.  In particular, our optimization procedure reduces
the size of the reach space of the closed loop system, while maintaining
other dynamical properties of interest (safety, stability, and response
time).

>>>>

We use a CounterExample-Guided Inductive Synthesis (CEGIS)~\cite{jha-icse10,
DBLP:conf/pldi/Solar-LezamaRBE05} approach, which we enhance with
abstraction refinement and optimization resulting in the novel CEGIS-OR
(CEGIS with Optimization and Refinement).  This design uses an iterative
process where each iteration performs inductive generalization based on
counterexamples provided by a verification oracle.  Essentially, the
inductive generalization uses information about a limited number of inputs
to make claims in the form of candidate solutions about all the possible
inputs.  By~using abstraction refinement, CEGIS-OR allows us to handle
complex systems, which are initially represented by coarse abstractions that
only get refined on demand.  Consequently, solutions that do not require a
high level of precision are obtained fast.  Since the use of coarse
abstractions may result in low-quality candidate solutions (i.e., candidates
that fail the specification on a very large number of inputs), we use
optimization techniques after each inductive generalization phase to improve
the produced candidates.  In particular, our optimization procedure reduces
the size of the reach space of the closed loop system, while maintaining
other dynamical properties of interest (safety, stability, and response
time).
